The Three Corridors

### 2015-01-10 msr.tex
adding text

@@

@@

\section{Harnessing Our Dataset}
\label{sec:exploit}

@@

The Java Platform exists more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications. The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition SDK. The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as {\sc jsr}s (Java Specification Requests), which are supported by prototype implementations.

@@

\cite{MKLGS14}

>>>>

Software metrics provide a means to extract useful and measurable information about the structure of a software system. Since software artefacts consist of digital data, many of their aspects are easily measured. This explains why the first metrics like LOC (Lines Of Code) and CLOC (Comment Lines of Code) appeared very early. Over the years, a wealth of different metrics has appeared in the literature \cite{GUSC07,BBM96,LOKI94,HK81,BDM97} and some of them, like Chidamber and Kemerer \cite{CHKE94} have found their way in software development practice and tools.

Today a software engineer or developer has a very large list of metrics at his disposition in order to gain the required insight for understanding and evaluating the size, complexity and overall structure of a system. This has led researchers to try to discover which set of metrics is most appropriate for each environment \cite{XSZC00,PUVA03,MAHA99,BRCA94}. There also exist metrics that can be used to evaluate other aspects of a system, such as the process that was used to develop it.

@@

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}.

  \item \textbf{JDepend} \textit{(jdep)}

  \item \textbf{CLMT} \textit{(clmt)}
\end{itemize}

@@

@@

The Java Platform exists more than a decade and provides a development environment for several application areas, such as web, grid computing, and traditional client-server applications. The official development environment of the Java platform is released by Oracle and is widely-known as the Java Standard Edition {\sc dsk}. The process of development and innovation in the Java ecosystem is built around a community, that writes proposals of features, known as {\sc jsr}s (Java Specification Requests), which are supported by prototype implementations.

@@

\cite{MKLGS14} \cite{KARA14}
